---
title: "REJSAMPLE AND MCMCSAMPLE"
author: "Valen Piotrowski"
date: "12/05/18"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#The 'rejsample' command allows a user to rejection sample from a given pdf.

INPUT DESCRIPTIONS:

n is the number of samples you want to pull from the pdf

pdf is the probability distribution function to sample from

a is the lower bound to sample from the pdf

b is the upper bound to sample from the pdf

C is a number greater than or equal to f(x) for all x


#Example:
```{r}
#This example gets 5 samples between 0 and 3 from the pdf x/2.
library(gitprobability)
pdf<-function(x){x/2}
rejsample(5, pdf, 0, 3, .4)
```

#The 'mcmcsample' command allows a user to get an MCMC sample from a given pdf.

INPUT DESCRIPTIONS:

t is a sample of numbers for the pdf to choose from

pdf is a random variable

#Example:
```{r}
#This example gets a sample from pdf x/2 between 0 and 2.
library(gitprobability)
pdf<-function(x){x/2}
t<-runif(1, 0, 2)
mcmcsample(t, pdf)
```

