---
title: "Rejsample"
author: "Valen Piotrowski"
date: "12/05/18"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#The 'rejsample' command allows a user to rejection sample from a given pdf.

#INPUT DESCRIPTIONS:

#n is the number of samples you want to pull from the pdf
#pdf is the probability distribution function to sample from
#a is the lower bound to sample from the pdf
#b is the upper bound to sample from the pdf
#C is a number greater than or equal to f(x) for all x

#Example:
```{r}
rejsample<-function(n, pdf, a, b, C){
  accepted<-0
  samp<-rep(NA,n)
  while(accepted<n){
  u<-runif(1,a,b)
  v<-runif(1,0,C)
  if(pdf(u)>=v){
    accepted<-accepted+1
    samp[accepted]=u
  }}
  samp}
#skip above if package is already installed
pdf<-function(x){x/2}
rejsample(5, pdf, 0, 3, .4)
```

#The 'mcmcsample' command allows a user to MCMC sample from a given pdf.

#INPUT DESCRIPTIONS:

# t is a sample of numbers for the pdf to choose from
# pdf is a random variable

#Example:
```{r}
mcmcsample<-function(t, pdf){
  dat<-t
  for(i in 1:0){
  proposed<-t
  if(runif(1,0,1)<pdf(proposed)/pdf(t)){t<-proposed}
  dat<-c(dat,t)
  }
  dat
}
#skip above if package is already installed
pdf<-function(x){x/2}
t<-runif(1, 0, 2)
mcmcsample(t, pdf)
```

